Positive Results in Registered Reports

### 2020-01-13 appendix/appendix.Rmd
added links to appendix

This document contains additional information about the methods and analyses reported in the manuscript '**An excess of positive results: Comparing the standard Psychology literature with Registered Reports**', as well as an additional robustness analysis (see section 4.1).

@@

Using a programming script written in Processing (The Processing Foundation, 2019) a single search query compatible with Web of Science was generated that contained the key phrase that had to occur in the paper ('test$^\ast$ the hypothes$^\ast$'), as well as the desired publication years (2013 up to and including 2018), and the ISSNs of all 633 journals listed as Psychiatry/Psychology journals in the ESI database (the journal list is provided in the file `raw_data/source_data/ESI_journallist_Psychology_20181204.xlsx`). 
The resulting search query is available in the file `raw_data/source_data/SR_search_query_WoS.txt`.

The search yielded 1919 results which were exported and saved in the file `raw_data/source_data/SR_search_results_WoS_20190107.csv`. 
We randomly selected 150 papers from this list using the sample() function in R and the seed '20190120':
```{r eval=FALSE}
# Load all 1919 search results
allSRs <- read.csv("SR_search_results_WoS_20190107.csv")

@@

### 3.2.4 Additional measures
For the sake of completeness, we report all other recorded measures not described thus far in the following (*all* recorded measures are included and described in the dataset `raw_data/positive_results_in_registered_reports_masterfile_data.xlsx`).

>>>>

This document contains additional information about the methods and analyses reported in the manuscript '**An excess of positive results: Comparing the standard Psychology literature with Registered Reports**', as well as an additional robustness analysis (see section 4.1). This PDF was created in RMarkdown. The reproducible RMarkdown file, containing embedded code for the analysis in section 4.1, is available in our online repository at <https://osf.io/dbhgr> ([`appendix/appendix.Rmd`](https://osf.io/t4kc3/)).

@@

Using a programming script written in Processing (The Processing Foundation, 2019) a single search query compatible with Web of Science was generated that contained the key phrase that had to occur in the paper ('test$^\ast$ the hypothes$^\ast$'), as well as the desired publication years (2013 up to and including 2018), and the ISSNs of all 633 journals listed as Psychiatry/Psychology journals in the ESI database (the journal list is provided in the file [`raw_data/source_data/ESI_journallist_Psychology_20181204.csv`](https://osf.io/x938b/)). 
The resulting search query is available in the file [`raw_data/source_data/SR_search_query_WoS.txt`](https://osf.io/9xah6/).

The search yielded 1919 results which were exported and saved in the file [`raw_data/source_data/SR_search_results_WoS_20190107.csv`](https://osf.io/q5fgd/). 
We randomly selected 150 papers from this list using the sample() function in R and the seed '20190120':
```{r eval=FALSE}
# Load all 1919 search results
allSRs <- read.csv("SR_search_results_WoS_20190107.csv")

@@

### 3.2.4 Additional measures
For the sake of completeness, we report all other recorded measures not described thus far in the following (*all* recorded measures are included and described in the dataset [`raw_data/positive_results_in_registered_reports_data.xlsx`](https://osf.io/aqr2s/)).
